Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-05 paper/main.tex
restructuring of discussion of shortcomings

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe an abstract location (e.g. ) or a setting as whole
(e.g. ``in Greenbow'', ``in a disco'', ``the platoon wades through a rice
field''). They also comprise words that could count as a member of another
categories in case the narrator uses these words to indicate a switch from one
setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``near an old bus'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

% AO COPEs: intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for three reasons and thus are not included in
the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
disco'', ''black and white film recordings'') whereas a picture of the verbally
described scene would be perceptually richer,
% hierarchical categories
(b) they also comprise words that could count as a member of another category in
case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as teenager'', ``near an old bus'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.  cuts but in AO stimulus
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.
% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a
regressor of interest in any contrasts because nouns in this category were
usually big and heavy. In a serial stream of auditory information, participants
could perceive furniture-related nouns as either a geometry-defining local scene
element or as an isolated object. Hence we did not use this category as
regressor of interest to reduce noise.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.

@@

\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
Notably, we did not choose the categories that contained switches from one
setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
to contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
These categories were actually heterogeneous: they rarely contained whole (and
thus vague) descriptions of landscapes (e.g. ``in a football stadium'',
``Forrest is running through the jungle'') but mostly landmarks or buildings,
and also non-spatial cues.\todo{repeat examples from method section}.
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial cues.

% AO: stimulus categories
For example in the AO stimulus, nouns of the narrator that cue a switch to
another setting belong to different categories (s. above).\todo[inline]{Number
of events in which contrasts?}
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.\todo{cross-modal control contrasts; all negative results at moment
of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.

% future studies: stimulus material
Future studies should probably use a different narrative that models the feature
space of spatial information ``better'' (provides more events that are more
easily classified to belong to distinctive categories).

@@

% shortcomings
visual confounds all over the place; obvious solution: annotate frames and track
focus of attention (but gist of a frame vs. attentional focus)

Individual differences when seeing a whole picture with many features vs. serial
auditory stream of information providing incidental cues; spatial attention?

% further studies
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
okay...}

@@

>>>>

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe an abstract location (e.g. ) or a setting as whole
(e.g. ``in Greenbow'', ``in a disco'', ``the platoon wades through a rice
field''). They also comprise words that could count as a member of another
categories in case the narrator uses these words to indicate a switch from one
setting to another (e.g. ``Jenny as a teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``Jenny as a
teenager'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

@@

% AO COPEs: intro
In context of the AO stimulus, the categories \texttt{se\_new} and
\texttt{se\_old} were problematic for three reasons and thus are not included in
the primary contrast:
% sparse auditory, rich visually
(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
disco'', ''black and white film recordings'') whereas a picture of the verbally
described scene would be perceptually richer,
% hierarchical categories
(b) they also comprise words that could count as a member of another category in
case the narrator uses these words to indicate a switch from one setting to
another (e.g. ``Jenny as a teenager'')
% soundscapes forestalls narrator
(c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that already cue a change of settings.  cuts but in AO stimulus
% conclusion
Hence, we assumed contrasts that (exclusively) used these two categories would
induce noise and would be less successful in isolating the PPA.
% furniture
We did not use the category ``furniture'' (\texttt{furn}) as a
regressor of interest in any contrasts because nouns in this category were
usually big and heavy. In a serial stream of auditory information, participants
could perceive furniture-related nouns as either a geometry-defining local scene
element or as an isolated object. Hence we did not use this category as
regressor of interest to reduce noise.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with
moments of cuts and therefore possibly correlated with a accompanying change in
the soundscape.

@@

\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
We did not choose the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
The categories \texttt{se\_new} and \texttt{se\_old} were actually
heterogeneous: they rarely contained whole and thus a vague verbal descriptions
of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
jungle'') but mostly landmarks or buildings, and also non-spatial
cues (e.g. ``Jenny as a teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial cues.

% future studies
Futures studies should chose a auditory narrative that better samples the
feature space correlating with the brain process to be investigated.
% future studies: stimulus material
Future studies should probably use a different narrative that models the feature
space of spatial information ``better'' (provides more events that are more
easily classified to belong to distinctive categories).

\tod[inline]{hypothesis of increased activation correlation with changes in the
    soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
    \texttt{pe\_old}).
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.

@@

\todo[inline]{imo opening the pandora's box of the AV shortcomings especially at
the end of the paper should be kept to a minimum of text}

% focus of study
The focus of the current study was to investigate if signficantly increased
hemodynamic activity in the PPA correlates with spatial information (compared to
``non-spatial'' information) during a naturalistic auditory stimulus.
% shortcomings
Results of the AV stimulus that we ran as a conceptual control are tempered by
using different kind of movie cuts regardless of the visual content of the movie
frame after the respective cuts.
% which leads to the ``blurred'' results
Hence we got visual confounds / clusters extending in to early visual areas.
% further studies
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.
% solution
Future studies that aim to use a movie to localize different visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

@@

% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.
